### 2014-09-18 sideband/obe/obe.tex
[sideband/obe]

>>>>

When only one sideband is driven,
\eqar{
  \Omega_{mn}=&\Omega_{m}\delta_{m,n-\Delta}+\Omega_{n}\delta_{n,m-\Delta}
}
where $Delta$ include both the change in vibrational level and internal level.\\
With $p_n=\rho{nn}$, the equations becomes,
\eqar{
  \pdiff{p_{m}}{t}=&\sum_k\paren{p_{k}\Gamma_{mk}-p_{m}\Gamma_{km}}+\ui\paren{\rho_{m,m-\Delta}\Omega_{m-\Delta}-\Omega_{m}\rho_{m+\Delta, m}+\rho_{m,m+\Delta}\Omega_{m}-\Omega_{m-\Delta}\rho_{m-\Delta,m}}\\
  \pdiff{\rho_{m,m+\Delta}}{t}=&-\frac{\rho_{m,m+\Delta}}{2}\sum_k\paren{\Gamma_{km}+\Gamma_{k,m+\Delta}}+\ui\Omega_{m}\paren{\rho_{mm}-\rho_{m+\Delta,m+\Delta}}
}
$\rho_{mn}$'s with $\abs{m-n}\neq0,\Delta$ are ignored since they are $0$. In particular, since $\Delta$ includes change of internal levels, elements with $\abs{m-n}\geqslant2\Delta$ does not exist.
